BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2015-03-31 Paper/D5.5/D5.5.tex
style des tables

\begin{table}
\centering
\begin{tabular}{|l|r|r|r|r|r|}
\hline
Image Size  & Naive (s) & Best (s) & Acceleration & BOAST (s) & Acceleration \\
\hline
768 x 432   & 0.0107    & 0.00669  & x1.6         & 0.000639  & x16.7 \\
\hline
2560 x 1600 & 0.0850    & 0.0137   & x6.2         & 0.00687   & x12.4 \\
\hline
2048 x 2048 & 0.0865    & 0.0149   & x5.8         & 0.00715   & x12.1 \\
\hline
5760 x 3240 & 0.382     & 0.0449   & x8.5         & 0.0325    & x11.8 \\
\hline
7680 x 4320 & 0.680     & 0.0747   & x9.1         & 0.0581    & x11.7 \\
\hline
\end{tabular}
\caption{Best performance of ARM Laplace kernel.}
\label{tbl:ARM}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{|l|r|r|r|r|r|}
\hline
Image Size & BOAST ARM (s) & BOAST Intel & Ratio & BOAST NVIDIA & Ratio \\
\hline
768 x 432   & 0.000639     & 0.000222    & x2.9  & 0.0000715    & x8.9  \\
\hline
2560 x 1600 & 0.00687      & 0.00222     & x3.1  & 0.000782     & x8.8  \\
\hline
2048 x 2048 & 0.00715      & 0.00226     & x3.2  & 0.000799     & x8.9  \\
\hline
5760 x 3240 & 0.0325       & 0.0108      & x3.0  & 0.00351      & x9.3  \\
\hline
7680 x 4320 & 0.0581       & 0.0192      & x3.0  & 0.00623      & x9.3  \\
\hline
\end{tabular}
\caption{Best performance of Laplace Kernel on several architectures.}
\label{tbl:other}
\end{table}

>>>>

\begin{table}
\centering
\begin{tabular}{c|r|r|c|r|c}
% \hline
  Image Size  & Naive (s) & Best (s) & Acceleration & BOAST (s) & Acceleration \\[4pt]
  \hline&&&&\\[-8pt]
768 x 432   & 0.0107    & 0.00669  & x1.6         & 0.000639  & x16.7 \\
% \hline
2560 x 1600 & 0.0850    & 0.0137   & x6.2         & 0.00687   & x12.4 \\
% \hline
2048 x 2048 & 0.0865    & 0.0149   & x5.8         & 0.00715   & x12.1 \\
% \hline
5760 x 3240 & 0.382     & 0.0449   & x8.5         & 0.0325    & x11.8 \\
% \hline
7680 x 4320 & 0.680     & 0.0747   & x9.1         & 0.0581    & x11.7 \\
% \hline
\end{tabular}
\caption{Best performance of ARM Laplace kernel.}
\label{tbl:ARM}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{c|r|r|c|r|c}
% \hline
  Image Size & BOAST ARM (s) & BOAST Intel & Ratio & BOAST NVIDIA & Ratio \\[4pt]
  \hline&&&&\\[-8pt]
768 x 432   & 0.000639     & 0.000222    & x2.9  & 0.0000715    & x8.9  \\
% \hline
2560 x 1600 & 0.00687      & 0.00222     & x3.1  & 0.000782     & x8.8  \\
% \hline
2048 x 2048 & 0.00715      & 0.00226     & x3.2  & 0.000799     & x8.9  \\
% \hline
5760 x 3240 & 0.0325       & 0.0108      & x3.0  & 0.00351      & x9.3  \\
% \hline
7680 x 4320 & 0.0581       & 0.0192      & x3.0  & 0.00623      & x9.3  \\
% \hline
\end{tabular}
\caption{Best performance of Laplace Kernel on several architectures.}
\label{tbl:other}
\end{table}
